---
title: "2019-04-01_Kahsay_31"
author: "Nicolas May"
date: "4/4/2019"
output: 
  html_document:
    theme: sandstone
    highlight: zenburn
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# BUILD DATASET

## Load Requirements

### Load Packages

```{r}
suppressMessages( library(dplyr)     )
suppressMessages( library(readr)     )
suppressMessages( library(stringr)   )
suppressMessages( library(lubridate) )
suppressMessages( library(tidyr)     )
```

### Load Useful Globals / Functions

```{r}
source("~/Desktop/config.R")
source("~/Desktop/helpers.R")

GET_API_DATA <- TRUE
```


## Get Data

### Define Data Fields/Forms

UDS 3

```{r}
# Form Header
fields_u3_hd_vct <-
  c(
    "ptid"
    , "dob"
    , "form_date"
  )

# Form A1
fields_u3_a1_vct <-
  c(
    "sex"        # 1 M, 2 F
    , "race"     # 1 Wht, 2 Blk, 3 AmI, 4 NH, 5 Asn, 50 Oth, 99 Unk
    , "handed"   # 1 L, 2 R, 3 A, 9 Unk
    , "educ"     # 
    , "maristat" # 
  ) %>% 
  c(., paste0("fu_", .), paste0("tele_", .))

# Form B6
fields_u3_b6_vct <- 
  c(
    "nogds"
    , "satis"
    , "dropact"
    , "empty"
    , "bored"
    , "spirits"
    , "afraid"
    , "happy"
    , "helpless"
    , "stayhome"
    , "memprob"
    , "wondrful"
    , "wrthless"
    , "energy"
    , "hopeless"
    , "better"
    , "gds"
  ) %>% 
  c(., paste0("fu_", .), paste0("tele_", .))

# Form C2
fields_u3_c2_vct <-
  c(
    "mocatots" # 1f. MOCA TOTAL RAW SCORE - UNCORRECTED
  )

# Form D1
fields_u3_d1_vct <-
  c(
    # Normal cognition
    "normcog"     # ivp_d1; 2. Does the subject have normal cognition?
    # Dementia
    , "demented"    # ivp_d1; 3. Does the subject meet criteria for dementia?
    , "amndem"      # ivp_d1; 4a. Amnestic multidomain dementia syndrome
    , "pca"         # ivp_d1; 4b. Posterior cortical atrophy syndrome
    , "ppasyn"      # ivp_d1; 4c. Primary progressive aphasia (PPA) syndrome
    , "ftdsyn"      # ivp_d1; 4d. Behavioral variant FTD syndrome
    , "lbdsyn"      # ivp_d1; 4e. Lewy body dementia syndrome
    , "namndem"     # ivp_d1; 4f. Non-amnestic multidomain dementia
    , "mciamem"     # ivp_d1; 5a. Amnestic MCI, single domain (aMCI SD)
    , "mciaplus"    # ivp_d1; 5b. Amnestic MCI, multiple domains (aMCI MD)
    , "mcinon1"     # ivp_d1; 5c. Non-amnestic MCI, single domain (naMCI SD)
    , "mcinon2"     # ivp_d1; 5d. Non-amnestic MCI, multiple domains (naMCI MD)
    , "impnomci"    # ivp_d1; 5e. Cognitively impaired, not MCI
    # Dementia etiology
    , "alzdis"      # ivp_d1; 11. Alzheimer's disease
    , "alzdisif"
    , "lbdis"       # ivp_d1; 12. Lewy body disease
    , "lbdif"
    , "msa"         # ivp_d1; 13. Multiple system atrophy
    , "msaif"
    , "cvd"         # ivp_d1; 15. Vascular Brain injury
    , "cvdif"
    , "esstrem"     # ivp_d1; 16. Essential tremor
    , "esstreif"
    , "downs"       # ivp_d1; 17. Down syndrom
    , "downsif"
    , "hunt"        # ivp_d1; 18. Huntington's disease
    , "huntif"
    , "prion"       # ivp_d1; 19. Prion disease
    , "prionif"
    , "brninj"      # ivp_d1; 20. Traumatic brain injury
    , "brninjif"
    , "hyceph"      # ivp_d1; 21. Normal-pressure hydrocephalus
    , "hycephif"
    , "epilep"      # ivp_d1; 22. Epilepsy
    , "epilepif"
    , "neop"        # ivp_d1; 23. CNS neoplasm
    , "neopif"
    , "hiv"         # ivp_d1; 24. Human immunodeficiency virus
    , "hivif"
    , "othcog"      # ivp_d1; 25. Cognitive impairment due to other not listed
    , "othcogif"
    , "dep"         # ivp_d1; 26. Active depression
    , "depif"
    , "bipoldx"     # ivp_d1; 27. Bipolar disorder
    , "bipoldif"
    , "schizop"     # ivp_d1; 28. Schizophrenia or other psychosis
    , "schizoif"
    , "anxiet"      # ivp_d1; 29. Anxiety disorder
    , "anxietif"
    , "delir"       # ivp_d1; 30. Delirium
    , "delirif"
    , "ptsddx"      # ivp_d1; 31. Post-traumatic stress disorder (PTSD)
    , "ptsddxif"
    , "othpsy"      # ivp_d1; 32. Other psychiatric disease
    , "othpsyif"
    , "alcdem"      # ivp_d1; 33. Cognitive impairment due to alcohol abuse
    , "alcdemif"
    , "impsub"      # ivp_d1; 34. Cognitive imp. due to other substance abuse
    , "impsubif"
    , "dysill"      # ivp_d1; 35. Cognitive impairment due to systemic disease
    , "dysillif"
    , "meds"        # ivp_d1; 36. Cognitive impairment due to medications
    , "medsif"
    , "cogoth"      # ivp_d1; 37. Cognitive impairment NOS
    , "cogothif"
    , "cogoth2"     # ivp_d1; 38. Cognitive impairment NOS
    , "cogoth2f"
    , "cogoth3"     # ivp_d1; 39. Cognitive impairment NOS
    , "cogoth3f"
  )

# Form iPad Tool Box
fields_u3_ipadtb_vct <-
  c(
    # NIH Toolbox
    "date"                     # admin date
    # , "tb_cardsortrawscore"    # TB CardSort RawScore
    # , "tb_flankerrawscore"     # TB Flanker RawScore
    # , "tb_listsortrawscore"    # TB ListSort RawScore
    # , "tb_oralrawscore"        # TB Oral RawScore
    # , "tb_patternrawscore"     # TB Pattern RawScore
    # , "tb_picseqrawscore"      # TB PicSeq RawScore
    # , "tb_picvocabrawscore"    # TB PicVocab RawScore
    # , "ipad_tool_box_complete" # TB complete?
    , "tb_cardsortage_corrected_standard_score"
    , "tb_cardsortcolumn1"
    , "tb_cardsortcolumn2"
    , "tb_cardsortcolumn3"
    , "tb_cardsortcolumn4"
    , "tb_cardsortcolumn5"
    , "tb_cardsortcomputed_score"
    , "tb_cardsortfully_corrected_t_score"
    , "tb_cardsortinstrumentbreakoff"
    , "tb_cardsortinstrumentrcreason"
    , "tb_cardsortinstrumentrcreasonother"
    , "tb_cardsortinstrumentstatus2"
    , "tb_cardsortitmcnt"
    , "tb_cardsortlanguage"
    , "tb_cardsortnational_percentile_age_adjusted"
    , "tb_cardsortrawscore"
    , "tb_cardsortse"
    , "tb_cardsorttheta"
    , "tb_cardsorttscore"
    , "tb_cardsortuncorrected_standard_score"
    , "tb_flankerage_corrected_standard_score"
    , "tb_flankercolumn1"
    , "tb_flankercolumn2"
    , "tb_flankercolumn3"
    , "tb_flankercolumn4"
    , "tb_flankercolumn5"
    , "tb_flankercomputed_score"
    , "tb_flankerfully_corrected_t_score"
    , "tb_flankerinstrumentbreakoff"
    , "tb_flankerinstrumentrcreason"
    , "tb_flankerinstrumentrcreasonother"
    , "tb_flankerinstrumentstatus2"
    , "tb_flankeritmcnt"
    , "tb_flankerlanguage"
    , "tb_flankernational_percentile_age_adjusted"
    , "tb_flankerrawscore"
    , "tb_flankerse"
    , "tb_flankertheta"
    , "tb_flankertscore"
    , "tb_flankeruncorrected_standard_score"
    , "tb_listsortage_corrected_standard_score"
    , "tb_listsortcolumn1"
    , "tb_listsortcolumn2"
    , "tb_listsortcolumn3"
    , "tb_listsortcolumn4"
    , "tb_listsortcolumn5"
    , "tb_listsortcomputed_score"
    , "tb_listsortfully_corrected_t_score"
    , "tb_listsortinstrumentbreakoff"
    , "tb_listsortinstrumentrcreason"
    , "tb_listsortinstrumentrcreasonother"
    , "tb_listsortinstrumentstatus2"
    , "tb_listsortitmcnt"
    , "tb_listsortlanguage"
    , "tb_listsortnational_percentile_age_adjusted"
    , "tb_listsortrawscore"
    , "tb_listsortse"
    , "tb_listsorttheta"
    , "tb_listsorttscore"
    , "tb_listsortuncorrected_standard_score"
    , "tb_oralage_corrected_standard_score"
    , "tb_oralcolumn1"
    , "tb_oralcolumn2"
    , "tb_oralcolumn3"
    , "tb_oralcolumn4"
    , "tb_oralcolumn5"
    , "tb_oralcomputed_score"
    , "tb_oralfully_corrected_t_score"
    , "tb_oralinstrumentbreakoff"
    , "tb_oralinstrumentrcreason"
    , "tb_oralinstrumentrcreasonother"
    , "tb_oralinstrumentstatus2"
    , "tb_oralitmcnt"
    , "tb_orallanguage"
    , "tb_oralnational_percentile_age_adjusted"
    , "tb_oralrawscore"
    , "tb_oralse"
    , "tb_oraltheta"
    , "tb_oraltscore"
    , "tb_oraluncorrected_standard_score"
    , "tb_patternage_corrected_standard_score"
    , "tb_patterncolumn1"
    , "tb_patterncolumn2"
    , "tb_patterncolumn3"
    , "tb_patterncolumn4"
    , "tb_patterncolumn5"
    , "tb_patterncomputed_score"
    , "tb_patternfully_corrected_t_score"
    , "tb_patterninstrumentbreakoff"
    , "tb_patterninstrumentrcreason"
    , "tb_patterninstrumentrcreasonother"
    , "tb_patterninstrumentstatus2"
    , "tb_patternitmcnt"
    , "tb_patternlanguage"
    , "tb_patternnational_percentile_age_adjusted"
    , "tb_patternrawscore"
    , "tb_patternse"
    , "tb_patterntheta"
    , "tb_patterntscore"
    , "tb_patternuncorrected_standard_score"
    , "tb_picseqage_corrected_standard_score"
    , "tb_picseqcolumn1"
    , "tb_picseqcolumn2"
    , "tb_picseqcolumn3"
    , "tb_picseqcolumn4"
    , "tb_picseqcolumn5"
    , "tb_picseqcomputed_score"
    , "tb_picseqfully_corrected_t_score"
    , "tb_picseqinstrumentbreakoff"
    , "tb_picseqinstrumentrcreason"
    , "tb_picseqinstrumentrcreasonother"
    , "tb_picseqinstrumentstatus2"
    , "tb_picseqitmcnt"
    , "tb_picseqlanguage"
    , "tb_picseqnational_percentile_age_adjusted"
    , "tb_picseqrawscore"
    , "tb_picseqse"
    , "tb_picseqtheta"
    , "tb_picseqtscore"
    , "tb_picsequncorrected_standard_score"
    , "tb_picvocabage_corrected_standard_score"
    , "tb_picvocabcolumn1"
    , "tb_picvocabcolumn2"
    , "tb_picvocabcolumn3"
    , "tb_picvocabcolumn4"
    , "tb_picvocabcolumn5"
    , "tb_picvocabcomputed_score"
    , "tb_picvocabfully_corrected_t_score"
    , "tb_picvocabinstrumentbreakoff"
    , "tb_picvocabinstrumentrcreason"
    , "tb_picvocabinstrumentrcreasonother"
    , "tb_picvocabinstrumentstatus2"
    , "tb_picvocabitmcnt"
    , "tb_picvocablanguage"
    , "tb_picvocabnational_percentile_age_adjusted"
    , "tb_picvocabrawscore"
    , "tb_picvocabse"
    , "tb_picvocabtheta"
    , "tb_picvocabtscore"
    , "tb_picvocabuncorrected_standard_score"
  )

# Concatenate field vectors
fields_u3_vct <- 
  c(
    fields_u3_hd_vct
    , fields_u3_a1_vct
    , fields_u3_b6_vct
    , fields_u3_c2_vct
    , fields_u3_d1_vct
    , fields_u3_ipadtb_vct
  )

# Collapse all fields
fields_u3 <- fields_u3_vct %>% paste(collapse = ",")
```

MiNDSet Registry

```{r}
# Registration Form
fields_ms_reg_vct <-
  c(
    "subject_id"
  )

fields_ms_dem_vct <-
  c(
    "county"
    , "race_value"
    , "ed_level"
    , "handedness"
  )

# Medical Visit Form
fields_ms_med_vct <-
  c(
    "exam_date"
  )

# Concatenate field vectors
fields_ms_vct <-
  c(
    fields_ms_reg_vct
    , fields_ms_dem_vct
    , fields_ms_med_vct
  )

# Collapse all fields
fields_ms <- fields_ms_vct %>% paste(collapse = ",")
```

### Retrieve Data via REDCap API

UDS3

MiNDSet Registry

### Retrieve Data from NACC Download CSVs

NACC Toolbox Data

```{r}
# Load `Assessment Data.csv`
df_asmnt_data <-
  read_csv("./NACC_iPad_data/Assessment Data.csv",
           col_types = cols(.default       = col_character()
                            , ADCID        = col_integer()
                            , INSTORDR     = col_integer()
                            , INSTSCTN     = col_integer()
                            , ITMORDR      = col_integer()
                            , SCORE        = col_number()
                            , THETA        = col_number()
                            , TSCORE       = col_number()
                            , SE           = col_number()
                            , RESPONSETIME = col_number()
                            ## MIXED DATETIME FORMATS!
                            ## YYYY-MM-DD
                            # , DATECREATED	= col_datetime("%Y-%m-%d %H:%M:%S")
                            # , INSTTARTED  = col_datetime("%Y-%m-%d %H:%M:%S")
                            # , INSTENDED   = col_datetime("%Y-%m-%d %H:%M:%S")
                            ## MM/DD/YYYY
                            # , DATECREATED	= col_datetime("%m/%d/%Y %H:%M:%S")
                            # , INSTTARTED  = col_datetime("%m/%d/%Y %H:%M:%S")
                            # , INSTENDED   = col_datetime("%m/%d/%Y %H:%M:%S")
           )) %>% 
  get_nonempty_fields()

# Split `df_asmnt_data` to correctly coerce datetime fields to datetime type
df_asmnt_data_1 <- df_asmnt_data %>% 
  filter(str_detect(DATECREATED, 
                    "\\d{4}-\\d{1,2}-\\d{1,2} \\d{1,2}:\\d{2}:\\d{2}") &
           str_detect(INSTTARTED,
                      "\\d{4}-\\d{1,2}-\\d{1,2} \\d{1,2}:\\d{2}:\\d{2}") &
           str_detect(INSTENDED,
                      "\\d{4}-\\d{1,2}-\\d{1,2} \\d{1,2}:\\d{2}:\\d{2}")) %>%
  mutate_at(vars(DATECREATED, INSTTARTED, INSTENDED),
            ~ as.POSIXct(as_datetime(.x, format = "%Y-%m-%d %H:%M:%S")))

df_asmnt_data_2 <- df_asmnt_data %>% 
  filter(str_detect(DATECREATED, 
                    "\\d{1,2}/\\d{1,2}/\\d{4} \\d{1,2}:\\d{2}"),
         str_detect(INSTTARTED, 
                    "\\d{1,2}/\\d{1,2}/\\d{4} \\d{1,2}:\\d{2}"),
         str_detect(INSTENDED, 
                    "\\d{1,2}/\\d{1,2}/\\d{4} \\d{1,2}:\\d{2}")) %>% 
  mutate_at(vars(DATECREATED, INSTTARTED, INSTENDED),
            ~ as.POSIXct(as_datetime(.x, format = "%m/%d/%Y %H:%M")))

df_asmnt_data_3 <- df_asmnt_data %>% 
  filter(is.na(DATECREATED) &
           is.na(INSTTARTED) &
           is.na(INSTENDED)) %>% 
  mutate_at(vars(DATECREATED, INSTTARTED, INSTENDED),
            ~ as.POSIXct(as_datetime(.x)))

# Recombine split `df_asmnt_data`
whole_split_diff <- nrow(df_asmnt_data) - sum(nrow(df_asmnt_data_1), 
                                              nrow(df_asmnt_data_2),
                                              nrow(df_asmnt_data_3))
if (whole_split_diff != 0) {
  stop("Some data in `df_asmnt_data` unaccounted for")
}
df_asmnt_data <- bind_rows(df_asmnt_data_1, 
                           df_asmnt_data_2,
                           df_asmnt_data_3)
rm(df_asmnt_data_1); rm(df_asmnt_data_2); rm(df_asmnt_data_3);

# Load `Assessment Scores.csv`
df_asmnt_scrs <-
  read_csv("./NACC_iPad_data/Assessment Scores.csv",
           col_types = cols(.default   = col_character()
                            , ADCID    = col_integer()
                            , RAWSCORE = col_number()
                            , THETA    = col_number()
                            , TSCORE   = col_integer()
                            , SE       = col_number()
                            , ITMCNT   = col_integer()
                            ## MIXED DATETIME FORMATS!
                            ## YYYY-MM-DD
                            # DATEFINISHED = col_datetime("%Y-%m-%d %H:%M:%S")
                            ## MM/DD/YYYY
                            # DATEFINISHED = col_datetime("%Y-%m-%d %H:%M:%S")
           )) %>% 
  get_nonempty_fields()

# Split `df_asmnt_scrs` to correctly coerce datetime fields to datetime type
df_asmnt_scrs_1 <- df_asmnt_scrs %>% 
  filter(str_detect(DATEFINISHED,
                    "\\d{4}-\\d{1,2}-\\d{1,2} \\d{1,2}:\\d{2}:\\d{2}")) %>% 
  mutate_at(vars(DATEFINISHED),
            ~ as.POSIXct(as_datetime(.x, format = "%Y-%m-%d %H:%M:%S")))

df_asmnt_scrs_2 <- df_asmnt_scrs %>% 
  filter(str_detect(DATEFINISHED,
                    "\\d{1,2}/\\d{1,2}/\\d{4} \\d{1,2}:\\d{2}")) %>% 
  mutate_at(vars(DATEFINISHED),
            ~ as.POSIXct(as_datetime(.x, format = "%m/%d/%Y %H:%M")))

df_asmnt_scrs_3 <- df_asmnt_scrs %>% 
  filter(is.na(DATEFINISHED)) %>% 
  mutate_at(vars(DATEFINISHED),
            ~ as.POSIXct(as_datetime(.x)))

# Recombine split `df_asmnt_scrs`
whole_split_diff <- nrow(df_asmnt_scrs) - sum(nrow(df_asmnt_scrs_1), 
                                              nrow(df_asmnt_scrs_2),
                                              nrow(df_asmnt_scrs_3))
if (whole_split_diff != 0) {
  stop("Some data in `df_asmnt_scrs` unaccounted for")
}
df_asmnt_scrs <- bind_rows(df_asmnt_scrs_1,
                           df_asmnt_scrs_2,
                           df_asmnt_scrs_3)
rm(df_asmnt_scrs_1); rm(df_asmnt_scrs_2); rm(df_asmnt_scrs_3);

df_asmnt_scrs <- df_asmnt_scrs %>% 
  mutate_at(vars(ends_with("_SCORE")),  as.numeric) %>% 
  mutate_at(vars(ends_with("_ADJ")),    as.numeric) %>% 
  mutate_at(vars(ends_with("_DOM")),    as.numeric) %>% 
  mutate_at(vars(ends_with("_NONDOM")), as.numeric) %>% 
  mutate_at(vars(ends_with("_P1")),     as.numeric) %>% 
  mutate_at(vars(ends_with("_LOGMAR")), as.numeric) %>% 
  mutate_at(vars(ends_with("_EAR")),    as.numeric) %>% 
  mutate_at(vars(INSTRUMENTBREAKOFF, INSTRUMENTSTATUS2, INSTRUMENTRCREASON),
            as.numeric)

# Load `Registration Data.csv`
df_regis_data <-
  read_csv("./NACC_iPad_data/Registration Data.csv",
           col_types = cols(.default = col_character()
                            , ADCID = col_integer()
                            , AGE = col_integer()
                            , EDUCATION = col_integer()
                            , GENDER = col_integer()
                            , HANDEDNESS = col_integer()
                            , RACE = col_integer()
                            , ETHNICITY = col_integer()
           )) %>% 
  get_nonempty_fields()
```


## Process Data

### Clean Data

UDS 3

MiNDSet Registry

NACC iPad Toolbox

```{r}
df_asmnt_data_cln <- df_asmnt_data %>% 
  select(-ADCID
         , -DEVICEID
         , -ASSESSMENTNAME
         , -INSTORDR
         , -INSTSCTN
         , -ITMORDR
         , -LOCALE
         , -DATATYPE
         , -APPVERSION
         , -IPADVERSION
         , -FIRMWAREVERSION)

df_asmnt_scrs_cln <- df_asmnt_scrs %>%
  select(-ADCID
         , -DEVICEID
         , -ASSESSMENTNAME
         , -LANGUAGE
         , -APPVERSION
         , -IPADVERSION
         , -FIRMWAREVERSION)

df_regis_data_cln <- df_regis_data %>% 
  select(-ADCID
         , -DEVICEID
         , -ASSESSMENTNAME)
```


### Mutate Data

UDS 3

MiNDSet Registry

NACC iPad Toolbox

```{r}
# Create date fields from a datetime fields
df_asmnt_data_cln_mut <- df_asmnt_data_cln %>% 
  mutate(DATE = as_date(INSTENDED)) %>% 
  select(-DATECREATED
         , -INSTTARTED
         , -INSTENDED)

df_asmnt_scrs_cln_mut <- df_asmnt_scrs_cln %>% 
  mutate(DATE = as_date(DATEFINISHED)) %>% 
  select(-DATEFINISHED)

# Propogate datetimes where missing
df_asmnt_scrs_cln_mut <- df_asmnt_scrs_cln_mut %>% 
  group_by(PIN) %>% 
  mutate(DATE = case_when(
    !is.na(DATE) ~ DATE,
    is.na(DATE) ~ max(DATE, na.rm = TRUE)
  )) %>% 
  ungroup()
```



### Reshape Data

NACC iPad Toolbox

```{r}
# Format from semi-long to wide

# `df_asmnt_data`
df_asmnt_data_cln_mut_lng <- df_asmnt_data_cln_mut %>% 
  mutate_all(as.character) %>% 
  gather(-PIN, -INST, -ITEMID, -DATE, key = "MEASURE", value = "VALUE")

df_asmnt_data_cln_mut_wide <- df_asmnt_data_cln_mut_lng %>%
  unite(col = "INST__ITEM__MEASURE", INST, ITEMID, MEASURE, sep = "__") %>%
  spread(key = INST__ITEM__MEASURE, value = VALUE) %>% 
  get_nonempty_fields()

write_csv(df_asmnt_data_cln_mut_wide, 
          "wide_data/df_asmnt_data_cln_mut_wide.csv",
          na = "")

# `df_asmnt_scrs`
df_asmnt_scrs_cln_mut_lng <- df_asmnt_scrs_cln_mut %>% 
  mutate_all(as.character) %>% 
  gather(-PIN, -INST, -DATE, key = "MEASURE", value = "VALUE")

df_asmnt_scrs_cln_mut_wid <- df_asmnt_scrs_cln_mut_lng %>% 
  unite(col = "INST__MEASURE", INST, MEASURE, sep = "__") %>% 
  spread(key = INST__MEASURE, value = VALUE) %>% 
  get_nonempty_fields()

write_csv(df_asmnt_scrs_cln_mut_wid,
          "wide_data/df_asmnt_scrs_cln_mut_wid.csv",
          na = "")
```



```{r echo=FALSE}
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
#  @##==---==##@##==---==##@    EXTRA  :  SPACE    @##==---==##@##==---==##@  #
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
#  @##==---==##@##==---==##@    EXTRA  :  SPACE    @##==---==##@##==---==##@  #
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
```
